---
title       : Motor Trend Car Road Tests Result
subtitle    : Change cylinders and displacement to get miles per gallon on car
author      : peikuo
job         : Coursera Assignment
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap, quiz, shiny, interactive]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}

--- .class #id 

## Choose number of cylinders and displacement
On the left panel, you can change this two paramenters
`r opts_chunk$set(echo=FALSE)`
```{r opts.label = 'shiny'}
require(slidify)
slidifyUI(
  fluidPage(
    titlePanel("Motor Trend Car Road Tests Result"),
    
    sidebarLayout(
      sidebarPanel(
        t("Choose number of cylinders and displacement to get the result of miles per gallon each car"),
        br(),
        br(),
        radioButtons("cyl", "Number of cylinders:",
                     c("4" = "4",
                       "6" = "6",
                       "8" = "8")
                     ),
        
        br(),
        
        sliderInput("range", "Displacement",
                    min = 60, max = 500, value = c(100,400)
                    ),
        br()
      ),
      mainPanel(
        tabsetPanel(type = "tabs", 
                    tabPanel("Plot Result", plotOutput("plot")), 
                    tabPanel("Table Result", tableOutput("table"))
        )
      )
    )
  )
)
        
```

--- .class #id 

## Miles per gallon on each car by barplot
After change parameters on the left, you can see result on the right shown by barplot

Barplot as below:

```{r}
par(mar=c(7,7,1,5))

barplot(mtcars$mpg, names.arg = rownames(mtcars), horiz = T, 
              cex.names = 0.9, las = 1, col=topo.colors(10), 
              xlab="Miles pre gallon")
```

--- .class #id 

## Miles per gallon on each car by Table
After change parameters on the left, you can see result on the right shown by table

Table as below:
```{r}
head(mtcars[, c("cyl", "disp", "mpg")], 8)
```

--- .class #id 
## Where to use this Application

Actually, this app is just a sample to use shiny for analysing data.
* In my app, my data is from the mtcars in package datasets
* In the future, change the dataset to get reactive result as you like

Wish you like this Application and have a happy hour